Towards Reliable Machine Learning Deployments in the Cloud

### 2023-12-12 paper.tex

\section{Results}
\cm{These are a brief overview of the results as I work on the plots and wait for the power data from Mohammad. Will add plots tonight, but you can see preliminary results in the plots folder. I'm still playing with how to squeeze all the data into a single page. I apologize for the delay.}

\subsection{Accuracy and Robustness}
Marginal gains in accuracy for faster hardware, but no significant change in survival time.
\subsection{Training Time}
Corresponds roughly to what we would expect from the peak GPU bandwidth numbers in Tab.~\ref{tab:hardware}.
\subsection{Latency}
Slower hardware is marginally slower. Results would be undetectable for a user with a reasonably small query.
\subsection{Monetary Cost}
Smaller hardware is significantly cheaper (roughly half the cost to train vs. the best hardware).
\subsection{Power}
Power tracks monetary cost closely, probably because that's the predominant cost for the datacenter itself~\cite{}.

@@

\newpage
\bibliographystyle{IEEEtran}
\bibliography{bibliography}
\vspace{12pt}

>>>>

\section{Results}
\cm{Here are most of the results. I'm still playing with how to 1. combine the hardware into a single model per dataset or 2. visualize 9 different combinations in a tiny space. I'd very much like to show the partial effects plots as I did before with the layers in the NEURIPS paper.}

\subsection{Accuracy and Robustness}
Marginal gains in accuracy for faster hardware, but no significant change in survival time.
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{plots/combined/acc.pdf}
    \caption{Ben. and Adv. Accuracy Across Datasets and Hardware}
    \label{fig:acc}
\end{figure*}

\subsection{Time}
Corresponds roughly to what we would expect from the peak GPU bandwidth numbers in Tab.~\ref{tab:hardware}.

Slower hardware is marginally slower. Results would be undetectable for a user with a reasonably small query.

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{plots/combined/time.pdf}
    \caption{Training, Prediction, and Attack times across datasets and hardware.}
    \label{fig:time}
\end{figure*}

\subsection{Monetary Cost}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{plots/combined/cost.pdf}
    \caption{Training, Prediction, and Attack Power Consumption Across Datasets and Hardware}
    \label{fig:time}
\end{figure*}
Smaller hardware is significantly cheaper (roughly half the cost to train vs. the best hardware).

\subsection{Power}
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{plots/combined/power.pdf}
    \caption{Training, Prediction, and Attack Power Consumption Across Datasets and Hardware}
    \label{fig:time}
\end{figure*}
Power tracks monetary cost closely, probably because that's the predominant cost for the datacenter itself~\cite{}.

\subsection{}

@@

% \newpage
\bibliographystyle{IEEEtran}
\bibliography{bibliography}
\vspace{12pt}
